---
title: "BIS15L_AI_hmwk"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions
This homework is a bit less traditional this week. There are some errors in the code below. In addition add notes and titles to the code chunks that explains what the code chunck does. Use AI tools, notes from class, or any other resources to help fix the errors. Feel free to edit any plots to your preference. Don't forget to answer the two questions at the bottom. Upon completion, you should not have to '#' out any of the code chunks.

Push your final work to your repository. Your final lab report should be organized, clean, and run free from errors. Remember, you must remove the `#` for the included code chunks to run. Be sure to add your name to the author header above.   

Again make sure to use the formatting conventions of RMarkdown to make your report neat and clean!  


```{r}
library(tidyverse)
library(janitor)
library(dplyr)
```


1.
```{r}
#this code chunk reads in a dataset and was originally mispelled and wasn't cleaned 
blood_count <- read_csv("data/blood_count_dataset.csv") %>% clean_names()
```
```{r}
getwd()
```

2. 
```{r}
glimpse(blood_count)
#glimpse allows you to get a short summary of your data and was misspelled 
```

3. 
```{r}
blood_count %>% 
  group_by(gender) %>% 
  summarize(min=min(red_blood_cells),
            mean=mean(red_blood_cells),
            max=max(red_blood_cells))
#this gets the mean of red blood cell counts and the maximum red blood cell count. 
#It was missing some commas and mean was misspelled
```


4. 
```{r}
options(scipen = 999, digits = 2)

blood <- blood_count %>% 
  filter(gender == "Male") %>%
  select(3:9) %>%
  colMeans(na.rm = TRUE)
#this gets a means of the columns for males 
#select should have been () instead of [] and M in male should have been capatalised as well as == instead of =
```

5. 
```{r}
blood_count %>% 
  filter(gender == "Female") %>%
  select(3:9) %>%
  colMeans(na.rm = T)
#mean of the colomns for females 
# () instead of []
# = instead of ==
# %>% instead of />%
#gender instead of Gender 
#blood instead of bloood 
```


6. 
```{r}

blood_count %>%
  pivot_longer(cols = (3:9), names_to = "test", values_to = "values") %>%
  ggplot(aes(x = gender, y = values, fill = gender)) +
  geom_boxplot() +
  facet_wrap(~test) 
  labs(title = "Boxplot of Blood Count Tests",
       x = "test",
       y = "values")
#pivot_longer not pivot_wider
#() not []
# needs facet_wrap 
#all lowercase columns 
#finds averges of the columns using boxplot 
```

7. 
```{r}
grouped_bc <- blood_count %>%
  mutate(age_group = case_when(
    age >= 20 & age <= 29 ~ "20s",
    age >= 30 & age <= 39 ~ "30s",
    age >= 40 & age <= 49 ~ "40s",
    age >= 50 & age <= 59 ~ "50s",
    age >= 60 & age <= 70 ~ "60s")) # there were only 4 people in 70s, so I combined it with 60s
grouped_bc
#adds age group
#a not A
#mutate not change
```

8. 
```{r}
grouped_bc %>%
  pivot_longer(cols = (3:9), names_to = "test", values_to = "values") %>%
  ggplot(aes(x = age_group, y = values, fill = age_group)) +
  geom_boxplot() +
  facet_wrap(~ test, scales = "free") +  # Facet by the "Test" variable
  labs(title = "Boxplot of Blood Count Tests by Age Group",
       x = "Age Group",
       y = "Values")

#plots for the distributions of the cols
#aes not ase
#grouped_bc not blood_count

```
9. What are two drawbacks and two benefits of AI?

AI could sifle learning if overused and could exaserbate plagarism at the same time it could make our
jobs alot easier by finding our mistakes and thinking of solutions before we can

10. Do you think you will use AI for coding in the future? Why or why not?

I might if I feel like i need to save time by having it do tetidous work for me 

## Push your final code to GitHub!
Please be sure that you check the `keep md` file in the knit preferences. 